---
title: "Leasing Market Survey"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Leasing Market Survey}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(gmhcommunities)
```

## Overview

To design a leasing market survey Shiny app for GMH Communities, we'll create a comprehensive web-based solution that replicates the structure and functionality of their existing spreadsheet-based survey. The app will allow General Managers to input weekly data for their properties and competitors, store historical information, and provide analysis tools for corporate staff.

## Key Components

1. User Interface
2. Market Survey Forms
3. Data Model
4. Analysis and Reporting

### User Interface (UI)

The app will be designed with a clean, modern interface that is easy to use 
and navigate. 

The main sections of the app will include a dashboard, market survey forms,
and survey insights & analysis tools.

#### R Shiny App Structure

The app will be built using the R Shiny framework, leveraging a modular
design to separate the UI and server logic into distinct components.

The app will consist of the following main sections or pages each with their 
own corresponding modules:

- Dashboard: Overview of properties and survey statuses
- Market Survey: Multi-tab interface for data entry survey form inputs
- Survey Insights: Analysis and reporting

### Market Survey Forms

The actual market survey is split into several sections, mirroring the 
original speadsheet-based survey data provided by GMH Communities.

Survey Sections:

- Property Summary & Image
- Leasing Summary
- Short Term Leases
- Fees
- Amenities (Property & Unit)
- Parking
- Utilities
- Office Hours
- Rents by Floor Plan
- Rents by Unit Type

plus an additional section for:

- Competitor Summary

Each section will be implemented as a separate Shiny module for maintainability
and re-usability.

### Data Model

The app will store survey data in a relational database, allowing for
historical data storage and analysis.

The data model specific the the market survey data will have its
own dedicated database schema: `mkt` and will consist of the following
core tables:

- `mkt.properties`: Core Property Information


- `mkt.property_summary`: Property-level static and descriptive fields from
  the *Property Summary* survey section.
- `mkt.leasing_summary`: Leasing-specific metrics updated weekly for the 
  *Leasing Summary* survey section.
- `mkt.short_term_leases`: Short-term lease information including availability and
  premiums for short-term leases for the *Short Term Leases* survey section.
  - `mkt.rents_by_floorplan`: 

